### 2017-11-07 submission/manuscript.Rmd
add supplemental legend 2 and 3

**Figure S2: **

**Figure S3: **

>>>>

**Figure S2: Random Forest Genus Model AUC for each Stool Study.** A) AUC of Adenoma models using all genera or CRC associated genera only. B) AUC of Carcinoma models using all genera or CRC associated genera only. The black line represents the median within each group.

**Figure S3: Random Forest Genus Model AUC for each Tissue Study.** A) AUC of Adenoma models using all genera or CRC associated genera only divided between matched and unmatched tissue. B) AUC of Carcinoma models using all genera or CRC associated genera only. The black line represents the median within each group divided between matched and unmatched tissue.

### 2017-11-07 submission/manuscript.tex
add supplemental legend 2 and 3

\textbf{Figure S2: }

\textbf{Figure S3: }

>>>>

\textbf{Figure S2: Random Forest Genus Model AUC for each Stool Study.}
A) AUC of Adenoma models using all genera or CRC associated genera only.
B) AUC of Carcinoma models using all genera or CRC associated genera
only. The black line represents the median within each group.

\textbf{Figure S3: Random Forest Genus Model AUC for each Tissue Study.}
A) AUC of Adenoma models using all genera or CRC associated genera only
divided between matched and unmatched tissue. B) AUC of Carcinoma models
using all genera or CRC associated genera only. The black line
represents the median within each group divided between matched and
unmatched tissue.
